---
title: "Ottr testing"
output:
  pdf_document: default
  html_notebook: default
---

Install [ottr](https://github.com/ucbds-infra/ottr):

```{r}
devtools::install_github("ucbds-infra/ottr@0.1.0")
```


## Some vectors

We might be interested in the change in [estimated average daily high
temperatures](http://berkeleyearth.lbl.gov/regions/global-land) over all land on
Earth (in degrees Celsius) for the decades surrounding 1850, 1900, 1950, and
2000.

From the link above, these values are:

* Decade surrounding 1850: 13.6
* Decade surrounding 1900: 14.39
* Decade surrounding 1950: 14.59
* Decade surrounding 2000: 15.16

Use the `c` function to make a new vector `mid_years` that contains these four
years, that are the centers of the decades.  For example, the first value in
`mid_years` should be 1850:

```{r}
#<- mid_years <- c(...)
mid_years <- c(1850, 1900, 1950, 2000)
#<->
# Show the values
mid_years
```

```{r}
# Run this chunk to check your answer
. = ottr::check("tests/mid_years.R")
```

Use the `c` function to make a new vector `high_temp` that contains these four corresponding temperature values.

```{r}
#<- high_temps <- ...
high_temps <- c(13.6, 14.39, 14.59, 15.16)
#<->
# Show the values
high_temps
```

```{r}
# Run this chunk to check your answer
. = ottr::check("tests/high_temps.R")
```